### 2019-07-09 2-Chapters/4-Chapter/chapter4.tex
Sent to my advisors, I'm printing it in 2 DAYS

After the first chapters that presented the model of MAB, we go back to the initial problems studied in this thesis, and thus we focus on Internet of Things (IoT) networks.
%
As explained in the introduction in Chapter~\ref{chapter:1},
unlicensed bands are more and more used and considered for mobile and LAN communication standards (WiFi, LTE-U), and for Internet of Things (IoT) standards for short-range (ZigBee, Z-Wave, Bluetooth) and long-range (LoRaWAN, SIGFOX, Ingenu, Weightless) communications \cite{Centenaro16}.
This heavy use of unlicensed bands, in particular with the expected exponential growth of the number of IoT devices, will cause performance drop, due to radio collisions that could even compromise IoT promises.

Efficient Medium Access (MAC) policies allow devices to avoid interfering traffic and can significantly reduce the spectrum contention problem in unlicensed bands.
As end-devices battery life is a key constraint of IoT networks,
and as IoT networks are decentralized, because the devices initiate transmissions,
this leads to IoT protocols using as low signaling overhead as possible and simple ALOHA-based mechanisms.
%
In this chapter, we analyze the performance of Multi-Armed Bandits (MAB) algorithms, that could be used in combination with a time-frequency slotted ALOHA-based protocol.
We highlight that even without changing anything on the level of IoT standards, our proposal is just an add-on capability that can be used on a unit-per-unit basis.
We consider the Upper-Confidence Bound (\UCB) \cite{Auer02}, and the Thompson-Sampling (TS) algorithms \cite{Thompson33,AgrawalGoyal11,
Kaufmann12Thompson}, for the first model. For the demonstration as well as for the second model, without loss of generality, we preferred to focus on heuristics based on the simplest algorithm (\ie, \UCB), to give a clear presentation of the different ideas explored to solve the problem of learning in order to retransmit efficiently.

@@

\textbf{Publications.}
%
This chapter is mainly based on our articles \cite{Bonnefoi17,Besson2018ICT,Besson2019WCNC,Bonnefoi2019WCNC,MoyBesson2019,MoyBesson2019Annales}.

>>>>

After the first chapters that presented the model of MAB, we go back to the initial problems studied in this thesis, and thus we focus on Internet of Things (IoT) networks.
%
As explained in the introduction in Chapter~\ref{chapter:1},
unlicensed bands are more and more used and considered for mobile and LAN (Local Area Network) and for Internet of Things communication standards.
%  (WiFi, LTE-U), (IoT) standards for short-range (ZigBee, Z-Wave, Bluetooth) and long-range (LoRaWAN, SIGFOX, Ingenu, Weightless) communications \cite{Centenaro16}.
This heavy use of unlicensed bands, in particular with the expected exponential growth of the number of IoT devices, will cause performance drop, due to radio collisions that could even compromise IoT promises.

Efficient Medium Access Control (MAC) policies allow devices to avoid interfering traffic and can significantly reduce the spectrum contention problem in unlicensed bands.
As end-devices battery life is a key constraint of IoT networks,
and as IoT networks are decentralized, because the devices initiate transmissions,
this leads to IoT protocols using as low signaling overhead as possible and simple ALOHA-based mechanisms.
%
In this chapter, we analyze the performance of Multi-Armed Bandits (MAB) algorithms, that could be used in combination with a time-frequency slotted ALOHA-based protocol.
We highlight that even without changing anything on the level of IoT standards, our proposal is just an add-on capability that can be used on a unit-per-unit basis.
We consider the \UCB \cite{Auer02}, and the Thompson-Sampling (TS) algorithms \cite{Thompson33,AgrawalGoyal11,
Kaufmann12Thompson}, for the first model. For the demonstration as well as for the second model, without loss of generality, we preferred to focus on heuristics based on the simplest algorithm (\ie, \UCB), to give a clear presentation of the different ideas explored to solve the problem of learning in order to retransmit efficiently.

@@

\paragraph{Publications.}
%
This chapter is mainly based on our articles \cite{Bonnefoi17,Besson2018ICT,Besson2019WCNC,Bonnefoi2019WCNC,MoyBesson2019,MoyBesson2019Annales}.
